% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Current} {Project Manager | Project Change Management}{PT Johnson Home Hygiene Products}{Jakarta}
    {November 2017} {PT Johnson Home Hygiene Products is group of multinational company, Sc. Johnson, with some of its famous brands are Baygon, Autan, Kiwi, and Bayclin.
                      \begin{itemize}
                        \item Managing 5-10 projects in a time, with various nationality project team member.                
                        \item Managing projects with net sales worth ranging from USD300K to USD 5.940MM.               
                        \item Successfully managing halal certification project for manufacturing site and Sc. Johnson products for Indonesia (first time for Sc. Johnson globally).              
                        \item Preventing sale lost USD 2300 per month, while handling carry over project for site moving and product rebranding.
                        \item Managing projects with products sold in multiple countries (global projects), with medium complexity.
                      \end{itemize}
                    }
                    {Project Management, Microsoft Project, Risk Analysis, Timeline Development}
  \emptySeparator
  \experience
    {Current} {Process Engineer | Project Change Management}{PT Johnson Home Hygiene Products}{Jakarta}
    {August 2016} {PT Johnson Home Hygiene Products is group of multinational company, (\href{https://www.scjohnson.com/}{Sc. Johnson}), with some of its famous brands are Baygon, Autan, Kiwi, and Bayclin.
                      \begin{itemize}
                        \item Process engineer for Asia’s countries projects.        
                        \item Running 15 - 18 projects at a time.
                        \item Process scale up, parameters setup, process improvement for mass production. 
                        \item Implementing SPC to control, monitor, and improve process.
                        \item New formula and material validation in lab. 
                        \item Work with government appointed lab to test product performance for registration.
                      \end{itemize}
                    }
                    {Product Development, Process Design, Process Validation, Process Improvement, Cleaning Validation, SAP, PLM, SPC}
  \emptySeparator
  \experience
    {July 2016} {Process Technologist}{PT Reckitt Benckiser Indonesia}{Bogor}
    {June 2015} {(\href{https://www.reckitt.com/}{PT Reckitt Benckiser Indonesia}) is group of multinational company from England, (\href{https://www.reckitt.com/}{Reckit}), with some its famous brands are Dettol, Strepsils, and Durex.
                      \begin{itemize}
                        \item Process scale up and process redesign for new products.        
                        \item Process and cleaning validation.
                        \item Successfully validating and improving newly build production facilities, with capacity three times bigger and with process automation.
                        \item Improving cleaning process to reduce energy and water used.
                      \end{itemize}
                    }
                    {Product Development, Process Design, Process Validation, Process Improvement, Cleaning Validation}
  \emptySeparator
  \experience
  {June 2015} {R\&D Group Leader}{PT Kao Indonesia Chemicals}{Karawang}
    {February 2012} {(\href{https://chemical.kao.com/id/}{PT Kao Indonesia Chemicals}) is group of multinational company from Japan, (\href{https://chemical.kao.com/global/}{Kao}), that produces raw materials for personal care products and industry related surfactants.
                      \begin{itemize}
                        \item Doing new formulation and reformulation for products to meet costumer’s needs.        
                        \item Technical support and technical sales for related products.
                        \item Successfully sale self developed new formula for coal mining industries to prevent self coal combustion.
                        \item Rewarded for successfully delivered sister’s company product to Indonesia, which open new business category for the company.
                      \end{itemize}
                    }
                    {R\&D, Product Development, Formulation, Technical Support}
\end{experiences}
